\appendix

\chapter{Appendix}

\chapterquote{Information is not knowledge.}{Albert Einstein}

\section*{Book creation details}

This book is a work in progress, developed iteratively in an agile fashion with new content added regularly. The creation process is open and transparent, utilizing \LaTeX{} for professional typesetting and version control through GitHub (\url{https://github.com/ctoframework/book}). A continuous integration (CI) pipeline ensures that every repository update triggers an automated build and publication of the latest version of the book.

\subsection*{Artificial Intelligence (AI) Assistance}

In the spirit of innovation and leverage---core tenets of this framework---the development of this book has been augmented by Artificial Intelligence (AI). AI tools were used to assist in brainstorming, research, draft generation, and linguistic polishing. However, all concepts, structure, and final technical decisions remain the responsibility of the author. This collaborative approach reflects the modern engineering practices discussed throughout the book: using advanced tools to amplify human expertise and deliver high-quality outcomes more efficiently.

\subsection*{Contributions}

Contributions from the community are highly encouraged. Whether you have ideas for new topics, spot typos, or have technical corrections, your input is vital to the evolution of this framework. Please submit your contributions via the standard pull request mechanism on GitHub.

\subsection*{License}

This book is distributed under the \booklicence. This license allows you to share and adapt the content as long as you attribute the author and share your contributions under the same license.
