\appendix

\chapter{Appendix}

\section*{Book creation details}

This book is a work in progress, developed iteratively in an agile fashion with new content added weekly. The creation process is open and transparent, utilizing \LaTeX{} for typesetting and version control through GitHub (\url{https://github.com/ctoframework/book}). Each new tag in the repository triggers an automatic publication of the latest version of the book.

Contributions are highly encouraged. Whether you have ideas, spot typos, or have fixes and corrections, your input is welcome. Please submit your contributions via the standard pull request mechanism on GitHub.

\subsection*{License}

This book is distributed under the \booklicence. This license allows you to share and adapt the content as long as you attribute the author and share your contributions under the same license.

\section*{About the author}

Santiago Lizardo is a technical leader with over 20 years of experience in the technology industry. He studied computing, mathematics, and statistics and has dedicated his most recent years to deepening his knowledge in leadership and management.

His extensive professional experience includes roles as CTO, software architect, and development team leader, where he has worked on defining and executing technological strategies for companies of various sizes and sectors.

He was the founder of two tech startups and has led development teams in software companies in Argentina, Spain, and the United Kingdom.

Currently, he serves as the Head of Engineering at a hardware and software company with a presence in the United Kingdom and the United States, where he applies the principles and practices presented in this book.
